Example script the `dispRity` paper

### 2018-03-02 paper/dispRity_paper.tex
acknowledgements up

\section{Acknowledgments}
Many thanks to Natalie Cooper for encouraging the development of this package and helping with the writing of this paper and the package manuals.
Thanks to David Bapst, Martin Brazeau, Andrew Jackson, Graeme Lloyd and Emma Sherratt for specific implementation ideas and to Michael Collyer, Gavin Simpson and two other anonymous reviewers for constructive and encouraging comments on the manuscript.
I acknowledge support from European Research Council under the European Union's Seventh Framework Programme (FP/2007 - 2013)/ERC Grant Agreement number 311092 awarded to Martin D. Brazeau and from the Discovery Project Grant DP170103227 awarded to Vera Weisbecker.

>>>>

\section{Acknowledgments}
Many thanks to Natalie Cooper for encouraging the development of this package and helping with the writing of this paper and the package manuals.
Thanks to David Bapst, Rompy Chompee, Martin Brazeau, Andrew Jackson, Graeme Lloyd and Emma Sherratt for specific implementation ideas and to Michael Collyer, Gavin Simpson and two other anonymous reviewers for constructive and encouraging comments on the manuscript.
I acknowledge support from European Research Council under the European Union's Seventh Framework Programme (FP/2007 - 2013)/ERC Grant Agreement number 311092 awarded to Martin D. Brazeau and from the Discovery Project Grant DP170103227 awarded to Vera Weisbecker.
